\documentclass[letterpaper,10pt]{article}

\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage[inline]{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{environ}
\usepackage{etoolbox}
\usepackage{fontawesome5}
%\usepackage{hrefs}

% Custom colors
\definecolor{darkblue}{RGB}{0,0,139}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
}

% Section formatting - REDUCED SPACING HERE
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & #4 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{2pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% REDUCED BULLET SPACING HERE
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt, parsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, itemsep=-1pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

% Removes page numbers
\pagestyle{empty}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE Tushar Nayak} \\ \vspace{5pt}
    \small (412) 478-5677 $|$ \href{mailto:tusharn@andrew.cmu.edu}{\underline{tusharn@andrew.cmu.edu}} $|$ 
    \href{https://linkedin.com/in/nayaktushar}{\underline{linkedin.com/in/nayaktushar}} $|$
    \href{https://tushar-nayak.github.io/}{\underline{tushar-nayak.github.io}}
\end{center}

\vspace{-3pt}
\noindent\small{
Machine Learning Engineer and Researcher focused on multimodal perception, geometric deep learning, and physics-informed learning. Building real-time systems for recovering spatial structure from sparse visual observations in medical imaging for robotics.
}
\vspace{-2pt}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Master of Science - Biomedical Engineering (Research)}{May 2026}
      \vspace{2pt}
      \resumeItemListStart
        \resumeItem{\textbf{Courses:} Computer Vision, Computational Modelling \& Analysis, Learning for 3D Vision, Medical Image Analysis}
        \resumeItem{\textbf{TA:} Computer Vision, Applied Deep Learning, ML in Biomedical Research, Fundamentals of Computational BME}
        \resumeItem{\textbf{Awards:} Carnegie Mellon University Biomedical Engineering Department Head's Fellowship}
      \resumeItemListEnd
      
    \resumeSubheading
      {Manipal Institute of Technology}{Manipal, India}
      {Bachelor of Technology - Biomedical Engineering, Minor in Data Science}{May 2023}
      \vspace{2pt}
      \resumeItemListStart
        \resumeItem{\textbf{Awards:} Best Paper - Second Intl. Conference on Artificial Intelligence, Computational Electronics \& Communication}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
% \section{Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, parsep=0pt]
%     \small{\item{
%      \textbf{Deep Learning}{: Graph Neural Networks, Neural ODEs, Attention Mechanisms, Physics-Informed Neural Networks, VLMs} \\
%      \textbf{3D Vision}{: Differentiable Neural Rendering, Deformable Registration, Implicit/Explicit Neural Representation, 3D Reconstruction} \\
%      \textbf{Vision}{: Object Detection, Segmentation, Structure From Motion, Optical Flow, Photometric Stereovision}} \\
%      \textbf{Frameworks}{: PyTorch, PyTorch3D, PyTorch Geometric, TorchDiffEq, TensorFlow, OpenCV, Scikit, CUDA, Docker, Git, Linux} \\
%      \textbf{Languages}{: Python, MATLAB, C, C++, R, Julia}}
%  \end{itemize}
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt]
\small\item{
\textbf{Deep Learning:} Transformers, GNNs, Neural ODEs, PINNs, Attention Mechanisms, VLMs \\
\textbf{3D Vision:} Reconstruction, Neural Rendering, Mesh/Point Cloud Processing, Deformable Registration, Implicit Representations \\
\textbf{Vision:} Detection, Segmentation, Multi-view Geometry, Camera Geometry, Optical Flow \\
\textbf{Frameworks:} PyTorch, PyTorch3D, PyG, TorchDiffEq, CUDA, OpenCV, Docker, Linux \\
\textbf{Languages:} Python, C++, R, MATLAB, Julia
}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Research}
  \resumeSubHeadingListStart

\resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Graduate Student Researcher, Computational Engineering \& Robotics Lab}{Aug 2024 -- May 2026}
      \resumeItemListStart
        \resumeItem{Architected \textsc{FluoroGRID}, a multi-modal framework fusing ResNet-based fluoroscopy encoder, PointNet-based mesh encoder, and dynamic Graph Convolutional Networks to estimate 3D deformation from 2D fluoroscopy images during endovascular surgery.}
        \resumeItem{Engineered a geometrically-regularized loss function embedding discrete differential geometry to enforce structural limits, achieving a sub-millimeter 3D target registration error (0.5mm) at an inference speed of 139 fps.}
        \resumeItem{Built a physics-grounded spatio-temporal synthetic data pipeline simulating temporal viscoelastic tool-tissue interaction meshes and simulated fluoroscopy ray-tracing, generating an expansive temporal dataset of 370,000+ paired 3D/2D training samples.}
      \resumeItemListEnd

    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Research Assistant, The $\forall$ Lab \& Image Science Lab }{Feb 2025 -- Aug 2025}
  \resumeItemListStart
    \resumeItem{Developed a Neural ODE-based forecasting pipeline to predict longitudinal glioblastoma growth using
  multimodal MRI sequences.}
    \resumeItem{Architected a hybrid Attention U-Net and temporal embedding model to evolve latent tumor states in continuous time.}
    \resumeItem{Presented findings at CMU BME Forum 2025, currently investigating tumor evolution as a more explicit dynamics problem.}
  \resumeItemListEnd


    \resumeSubheading
      {Manipal Institute of Technology}{Manipal, India}
      {Undergraduate Student Researcher, Biomedical Informatics Computing Lab}{Jan 2022 -- May 2023}
      \resumeItemListStart
        \resumeItem{Designed an ensemble neural network combining three transfer-learning models with self-attention for Oral Cancer detection.}
        \resumeItem{Achieved CAM visualizable accuracies of 95\% for detecting cancer across lesion photos, OCT, and histological modalities.}
        \resumeItem{Co-authored publications based on this pipeline, alongside related models for Lung Cancer, Monkeypox \& Dengue detection.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart


\resumeProjectHeading
    {\textbf{Sparse 2D Echocardiograph to 3D Cardiac Volume Reconstruction}}{}
    \resumeItemListStart
        \resumeItem{Developed a sparse-view 3D cardiac reconstruction pipeline using coordinate-based neural implicit representations to recover continuous volumetric cardiac ventricular occupancy fields from sparse (2--3) 2D echocardiography slices.}
        \resumeItem{Implemented differentiable multi-view projection with learnable pose optimization for joint slice alignment and geometry recovery, used Fourier positional encodings to capture fine anatomical detail and high-frequency boundaries under sparse supervision.}
        \resumeItem{Applied volumetric BCE point sampling to supervise unobserved 3D regions and geometric regularization (smoothness / surface priors) to enforce anatomically plausible reconstructions, achieving 3D Dice 0.864 and 3D IoU 0.765 on MITEA-CAP}
    \resumeItemListEnd
        \resumeProjectHeading
    {\textbf{Dual-View Mammography Breast Cancer Prediction}}{}
    \resumeItemListStart
        \resumeItem{Developed a spatial alignment pipeline to register MLO mammograms to CC view using breast-mask centroid matching and affine translation, for better dual-view feature correspondence by reducing cross-view centroid distance from 411 px to 0.39 px.}
        \resumeItem{Built a ResNet + cross-attention classifier that fused aligned mammograms for binary prediction at 80\% on CBIS-DDSM dataset.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Neural Anisotropic Diffusion Network for MRI Denoising}}{}
    \resumeItemListStart
        \resumeItem{Unrolled the Perona-Malik denoising PDE into a differentiable neural  network with learned spatially-adaptive conduction weights.}
        \resumeItem{Achieved 24.85 dB PSNR on Br35H dataset (+4.46 dB vs. classical baselines) while reducing Edge MSE by 47\%.}
    \resumeItemListEnd

          
    % \resumeItemListEnd
    %  \resumeProjectHeading
    %   {\textbf{Unsupervised Neural Active Contours for Segmentation}}{ }
    %   \resumeItemListStart
    %     \resumeItem{Developing an unsupervised pipeline for medical image segmentation using a CNN-driven Neural Active Contour framework to predict boundaries via a physics-inspired energy minimization and integrating Chan-Vese region priors}
    %   \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}